---
title: "Week-wise Agent Rank Correlation"
output: html_document

params:
  startdate:  'DATE_SUB(CURDATE(), INTERVAL 3 MONTH)'                            ##start date for report, interval can be changed if needed
  enddate: 'CURDATE()'                                                           ##end date
  tableName: '`mundiale_tfn.smetable_new2`'                                      ##table name
  programID: 'MundialeAYTY_TFN'                                                  ##programID
  
  sme_filter: "crm_lookup = 1 and leadlist_lookup = 1 and c_offer_type_CRM = 'PRE_CTRL' and skill is not null and skill <> 'NA' and tipo_de_ligacao = 'Preditivo' and nconnects_oth2 <> 'NA' and isrelevant = 1 and skill = '0024900024' "
               #sme filter in addition to callTime. Leave it empyt if there isn't any
               
  front_half_days: 15
  back_half_days: 15
  no_of_rolls: 15
  moving_window_days: 5
  
  
  
  variables: "week(calltime) as week, date(calltime) as date, calltime, agentid, issale" 
              ##add variables for which the correlation needs to be checked
  time_column: "calltime"
  
  fileName: "0024900024_Mundiale_Variable_Correlation_Matrix" #Output file name 

  database: "smexplorerdata" # Schema on ai server.
  user : 'mundiale_ai_user'
  pass : "#mundiale_ai_user#"
  host : '10.4.2.82'
  port : 3307




---

``````{r packages3, include=FALSE , warning=FALSE , message=FALSE}
##Loading essential libraries
  library(tidyverse)
  library(lubridate)
  library(dplyr)
  library(DBI)
  library(tidyr)
  library(RMySQL)
  library(data.table)
  library(stringr)
  library(modelr)
  library(scales)
  library(knitr)
  library(dbscan)
  library(formattable)
  library(matrixStats)
  library(corrplot)
```


```{r disconnect connections3, include=FALSE , warning=FALSE , message=FALSE}
all_cons <- dbListConnections(MySQL())
# print(all_cons)
for(con in all_cons)
  +  dbDisconnect(con)
```


```{r SmeQuery3 , include=FALSE , echo=FALSE , warning=FALSE , message=FALSE}

SmeQuery <- function(params){
    
    my_query = paste0("select " , params$variables, " from " ,params$tableName,
                      " where ",  params$sme_filter, " and ", params$time_column, " between " ,params$startdate, " and " , params$enddate, "order by date desc")
    return(my_query)
  }
```


```{r get_data3 , include=FALSE, echo=FALSE  , warning=FALSE , message=FALSE}

my_query <- SmeQuery(params)

MySQLConnect216AI <- dbConnect(dbDriver("MySQL"),user=params$user, password=params$pass,
                               dbname=params$database, host=params$host, port = params$port)


VARNAME <- dbGetQuery(MySQLConnect216AI, my_query); 

on.exit(dbDisconnect(MySQLConnect216AI))

dist=as.data.frame(VARNAME)

data = dist
data$date = ymd(data$date)
setnames(data, tolower(names(data)))

```

```{r corr_calculation3, include=FALSE, echo=FALSE  , warning=FALSE , message=FALSE  }

data1 = data %>% group_by(week,agentid) %>% summarise(offcr = mean(issale))
matrix = dcast(data1, week~agentid, value.var="offcr" , fill = 0)
matrix2 = data.matrix(matrix, rownames.force = NA)
matrix3 = rowRanks(matrix2, rows = NULL, cols = c(2:ncol(matrix2)), ties.method = c("max",
                                                      "average", "first", "last", "random", "max", "min", "dense"),
         dim. = dim(matrix2))

matrix4 = t(matrix3)
corr = cor(matrix4)
rownames(corr) = matrix$week
colnames(corr) = matrix$week

data2 = data %>% filter(date >= Sys.Date() - 8)
data2 = data2 %>% group_by(date,agentid) %>% summarise(offcr = mean(issale))
matrix = dcast(data2, date~agentid, value.var="offcr" , fill = 0)
matrix2 = data.matrix(matrix, rownames.force = NA)
matrix3 = rowRanks(matrix2, rows = NULL, cols = c(2:ncol(matrix2)), ties.method = c("max",
                                                      "average", "first", "last", "random", "max", "min", "dense"),
         dim. = dim(matrix2))

matrix4 = t(matrix3)
corr1 = cor(matrix4)
rownames(corr1) = 1:length(matrix$date)
colnames(corr1) = 1:length(matrix$date)


tile = floor(length(unique((data$date)))/15)

data$ntile = ntile(data$date,tile)
data_dates = data %>% group_by(ntile) %>% summarise(max_date = max(date), min_date = min(date))
data_dates$date_range = paste0(as.character(data_dates$min_date), " - ", as.character(data_dates$max_date))

data3 = data %>% group_by (ntile,agentid) %>% summarise(offcr = mean(issale))
matrix = dcast(data3, ntile~agentid, value.var="offcr" , fill = 0)
matrix2 = data.matrix(matrix, rownames.force = NA)
matrix3 = rowRanks(matrix2, rows = NULL, cols = c(2:ncol(matrix2)), ties.method = c("max",
                                                      "average", "first", "last", "random", "max", "min", "dense"),
         dim. = dim(matrix2))

matrix4 = t(matrix3)
corr2 = cor(matrix4)
rownames(corr2) = as.character(data_dates$date_range)
colnames(corr2) = as.character(data_dates$date_range)

j = 0
z = min(data$date)
max_date_bh = max(data$date)
max_date_data = max_date_bh
data_fh_bh = data.frame(fh_date=character(), bh_date = character(), correlation = numeric())

for (i in 1:params$no_of_rolls){
 
  
  data_fh = data %>% filter( date >= z + j,   date <= params$front_half_days + j + z )
  data_bh = data %>% filter(date >= params$front_half_days + j + z + 1, date <= params$back_half_days + params$front_half_days + j + z + 1 )
  max_date_fh = max(data_fh$date)
  if(z + j + j > max_date_data | params$front_half_days + j + j + z + 1 > max_date_data) {break}
  # data_fh = data[(z+j):(params$front_half_days + j + z),]
  # data_bh = data[(params$front_half_days + j + z + 1):(params$back_half_days + params$front_half_days + j + z + 1),]
  z  =  z + j
  j  =  params$moving_window_days
  
  data_fh$date_range = paste0(min(data_fh$date), " - ", max(data_fh$date))
  data_fh = data_fh %>% group_by(date_range, agentid) %>% summarise(offcr = mean(issale))
  
  data_bh$date_range = paste0(min(data_bh$date), " - ", max(data_bh$date))
  data_bh = data_bh %>% group_by(date_range, agentid) %>% summarise(offcr = mean(issale))
  
  data_comb = rbind(data_fh,data_bh)  

  matrix = dcast(data_comb, date_range~agentid, value.var="offcr" , fill = 0)
  matrix2 = data.matrix(matrix, rownames.force = NA)
  matrix3 = rowRanks(matrix2, rows = NULL, cols = c(2:ncol(matrix2)), ties.method = c("max",
                                                      "average", "first", "last", "random", "max", "min", "dense"),
         dim. = dim(matrix2))

matrix4 = t(matrix3)
corr3 = cor(matrix4)
# rownames(corr3) = as.character(matrix$date_range)
# colnames(corr3) = as.character(matrix$date_range)
data_fh_bh_temp = data.frame(fh_date =  data_fh$date_range[1], bh_date = data_bh$date_range[1], correlation =  corr3[1,2] )

data_fh_bh = rbind(data_fh_bh, data_fh_bh_temp)

# data_fh_bh[1,1] = data_fh$date_range[1]
# data_fh_bh[1,2] = data_bh$date_range[1]
# data_fh_bh[1,3] = corr3[1,2]



}






```



## Week-wise Correlation
```{r plot3, echo=FALSE  }

corrplot(corr, method = "color" , type = "lower", addCoef.col = "black")


```


## 15-day-wise Correlation
```{r plot4, echo=FALSE  }


corrplot(corr2, method = "color" , type = "lower", addCoef.col = "black")

```


## L7_Days Correlation
```{r plot5, echo=FALSE  }


corrplot(corr1, method = "color" , type = "lower", addCoef.col = "black")

```

## Moving FHBH Correlation
```{r plot6, echo=FALSE  }


formattable(data_fh_bh , align = "l") 

```