---
title: "GKTAU Variable Correlation"
output: html_document
params:
  startdate:  'DATE_SUB(CURDATE(), INTERVAL 60 DAY)'                            ##start date for report
  enddate:    'CURDATE()' ##end date, interval can be changed if needed
  tableName:  '`mundiale_tfn.smetable_new2`'     ##table name
  programID:  'MundialeAYTY_TFN'
  
  
  sme_filter: "skill in ('0024900024') and crm_lookup = 1 and leadlist_lookup = 1 and c_offer_type_CRM = 'PRE_CTRL' and skill is not                   null and on_off = 0 and skill <> 'NA' and tipo_de_ligacao = 'Preditivo' and nconnects_oth2 <> 'NA'"
               #sme filter in addition to callTime. Leave it empyt if there isn't any
  
  variables: "C_TMP_BASE_CRM, C_TECNOLOGIA_RESUMO_CRM, C_Age_CRM, C_QT_DURC_TRFD_CRM, M_FIELD_2_LL, M_FILLER_LL, nConnectsRollUp_OTH3" 
              ##add variables for which the correlation needs to be checked
  
  ##the variables that are alphanumeric or have special characters or have NA's or nulls will be marked true in is_factor             
  is_factor: ["F","T","T","F","T","T","F","T"] 
  is_char:   ["T","T","T","T","T","T","T","F"]    ##all the variables that are not integer will be marked true
  is_int:    ["T","T","T","T","T","T","T","F"]    ##all the variables that are not integer will be marked true
  is_bin:    ["T","F","T","T","F","F","T","F"]    ##the variables that are required to be binned will be marked true
  is_cor:    ["T","T","T","T","T","T","T","F"]    ##the variables that will be taken into account for correlation must be marked true
  is_class_imbalance: ["T"]                       ##if there is class imbalance in optimization metric than mark true
  
  bin_type: ["quantile","","quantile","kmeans","","","kmeans",""]

  optimizationmetric: "issale"                    ##enter optimization metric
  ## provide bin type for which is_bin is true, enter "" in position of variable where binning not required
  
  time_column: "calltime"
  
  database: "smexplorerdata" # Schema on ai server.
  user : 'mundiale_ai_user'
  pass : "#mundiale_ai_user#"
  host : '10.4.2.82'
  port : 3307

---



``````{r packages, include=FALSE , warning=FALSE , message=FALSE}
##Loading essential libraries
  library(GoodmanKruskal) ## code would not run without this libraary
  library(classInt)       ## code would not run without this libraary
  library(dplyr)
  library(RMySQL)
  library(data.table)
  library(knitr)
  library(lubridate)
  library(smotefamily)
  library(formattable)
```




```{r disconnect connections, include=FALSE , warning=FALSE , message=FALSE}
all_cons <- dbListConnections(MySQL())
# print(all_cons)
for(con in all_cons)
  +  dbDisconnect(con)
```


```{r SmeQuery , include=FALSE , echo=FALSE , warning=FALSE , message=FALSE}

SmeQuery <- function(params){
    
    my_query = paste0("select " , params$variables, "," ,params$optimizationmetric, " as opt_metric from " ,params$tableName,
                      " where ",  params$sme_filter, " and ", params$time_column, " between " ,params$startdate, " and " , params$enddate)
    return(my_query)
  }
```

```{r get_data , include=FALSE, echo=FALSE  , warning=FALSE , message=FALSE}

my_query <- SmeQuery(params)

MySQLConnect216AI <- dbConnect(dbDriver("MySQL"),user=params$user, password=params$pass,
                               dbname=params$database, host=params$host, port = params$port)


VARNAME <- dbGetQuery(MySQLConnect216AI, my_query); 

on.exit(dbDisconnect(MySQLConnect216AI))

dist=as.data.frame(VARNAME)

data = dist
setnames(data, tolower(names(data)))

```



```{r data_preproc , include=FALSE, echo=FALSE  , warning=FALSE , message=FALSE}

##this part need to be modified if using different variables having various types

is_factor = as.logical(as.vector(unlist(params$is_factor)))
is_char = as.logical(as.vector(unlist(params$is_char)))
is_int = as.logical(as.vector(unlist(params$is_int)))
is_bin = as.logical(as.vector(unlist(params$is_bin)))
is_cor = as.logical(as.vector(unlist(params$is_cor)))
is_class_imbalance = as.logical(as.vector(unlist(params$is_class_imbalance)))   
bin_type = as.character(as.vector(unlist(params$bin_type)))



data_proc = data              ## copying the original dataframe, data_proc will contain the transformed data

## following loop will factorize the required variables and convert the characters variables to numeric

for (i in 1:(length(data_proc))){
  if (is_char[i] == TRUE){
    data_proc[[i]] = as.character(unlist(data_proc[[i]]))
  }
  
  if (is_factor[i] == TRUE){
    data_proc[[i]] = factor(data_proc[[i]])
  }
  
  if (is_int[i] == TRUE){
    data_proc[[i]] = as.numeric(data_proc[[i]])
  }
}


## following funtion will account for class imbalance in opt_metric by synthetically oversampling the minority class, this may take some time depending upon the size of data

data_proc = na.omit(data_proc)

if (is_class_imbalance[1]){
  
  data_smote  = smotefamily::SMOTE(data_proc[,1:7],data_proc$opt_metric, K=4, dup_size = 0  ) ## the values for K can be changed ## 7:35
  data_proc_smote = data_smote$data
  data_proc_smote$class = as.numeric(data_proc_smote$class)   
  data_proc_smote_grp = data_proc_smote 
  
} else {
  
   data_proc_smote = data_proc
   data_proc_smote_grp = data_proc
}



## following part will create binning of variables based on GroupNumeric function 



for (i in 1:(length(data_proc_smote_grp))){
  
  if (is_bin[i]){
    data_proc_smote_grp[[i]] = GroupNumeric(data_proc_smote_grp[[i]], n=5, style = bin_type[i]) 
    
    #make sure is_bin and bin_type values are correct 
    }
}


```



```{r GKTau_Corr , include=FALSE, echo=FALSE  , warning=FALSE , message=FALSE}
##corr_raw will calculate correlation on the raw variables

corr_raw <- data.frame(
  Variables = colnames(data_proc_smote[,1:(length(is_cor)-1)]),
  correlation_perc_raw = vector(mode = 'numeric', length = (length(is_cor))-1)
)

for (i in 1:(length(is_cor))){
  if(is_cor[i] == TRUE){
    x = (GKtau(data_proc_smote[[i]],data_proc_smote[[8]]))
    corr_raw[i,2] = (as.numeric(x$tauxy))*100
  }
}


##corr_grp will calculate correlation on binned groupnumeric binned variables 


corr_grp <- data.frame(
  Variables = colnames(data_proc_smote_grp[,1:(length(is_cor)-1)]),
  correlation_perc_bin = vector(mode = 'numeric', length = (length(is_cor))-1)
)

for (i in 1:(length(is_cor))){
  if(is_cor[i] == TRUE){
    x = (GKtau(data_proc_smote_grp[[i]],data_proc_smote_grp[[8]]))
    corr_grp[i,2] = (as.numeric(x$tauxy))*100
  }
}
```

# GK-Tau Variable Correlation
```{r plot , echo=FALSE  }

corr_raw= as.data.frame(corr_raw)
corr_grp= as.data.frame(corr_grp)

corr_grp = formattable(corr_grp, list(area(col = correlation_perc_bin) ~ color_tile("transparent", "green")))
corr_raw = formattable(corr_raw, list(area(col = correlation_perc_raw) ~ color_tile("transparent", "pink")))

corr_grp[order(-corr_grp$correlation_perc_bin),]
corr_raw[order(-corr_raw$correlation_perc_raw),]



##corr_tot <- merge(corr_grp,corr_raw,by=c("Variables"))
##corr_tot = formattable(corr_tot, list(area(col = correlation_perc_bin:correlation_perc_raw) ~ color_tile("transparent", "green")))
##corr_tot = corr_tot[order(-corr_tot$correlation_perc_bin),]
##corr_tot
```

